---
title: "311 Calls - 607 final project"
author: "Chunmei Zhu and John Wong"
date: "November 26, 2017"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
      
---


```{r}
#Download required packages
library(XML)
library(RCurl)
library(xlsx)
library(rvest)
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(wordcloud)
```

#Data Source 

download data from NYC govement open data

311 Service Requests from 2010 to Present  https://data.cityofnewyork.us/dataset/311-Service-Requests-From-2011/fpz8-jqf4
Median Household Income 2017 by zip code http://zipatlas.com/us/ny/zip-code-comparison/median-household-income.htm
NYC Weather, search New York, NY for area of interest  https://www.ncdc.noaa.gov/cdo-web/confirmation


Transformed data- CleanZipCodePerDayComplaintFreq.txt 


```{r}

#Data set: we need to create a table which contains daily weather, complaint types by zip code. 

#Prepare raw data sets: read in csv or txt files into R 

raw_call311_2013to2017 <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/CleanZipCodePerDayComplaintFreq.txt", header=TRUE, sep=",")

raw_nyc_zipcode <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/Zipcode_tidy.csv", header=TRUE, sep=",")

```


###Clean Zip Codes

```{r}
#Clean Zip Code: filter 311 Calls insident zip code by New York zip code table 
zipCode <- raw_nyc_zipcode$Zip.Code

```


#Total Complaint Types Word Cloud

```{r }
word_count <- raw_call311_2013to2017 %>%
  drop_na() %>%
  filter(Type != "TAVG") %>%
  group_by(Type) %>%
  summarize(
    freq = sum(Freq)
  )

set.seed(1234)
wordcloud(words = word_count$Type, freq = word_count$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.1 
          )

```



#Top 20 complaint types from 2011 to 2017


```{r}

# Read CSV into R
top20types <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/combine.txt", header=TRUE, sep=",")

top20Total <- top20types %>%
  select(Type,SubTotal)%>%
  drop_na() %>%
  group_by(Type) %>%
  summarize(
    Total = sum(SubTotal)
  )%>%
  arrange(-Total)%>%
  top_n(n = 20, Total)

ggplot(top20Total, aes(x=top20Total$Type, top20Total$Total, color=top20Total$Total)) + geom_bar(stat = "identity",fill='lightblue', color="lightblue") + xlab("Complaint Types") +
  ylab("Frequency") + 
  theme(axis.text.x=element_text(angle=90,hjust=0.2,vjust=0.2))

```


#General correlation analysis for complain types


```{r}
#transfor long form to wide form
wide_top20types <- spread(top20types,Type,SubTotal)
#wide_top20types 

wide_top20types <- wide_top20types[,2:23]


#calculate correlation matrix
res <- cor(wide_top20types, use = "complete.obs")
round(res, 2)


library(corrplot)

# correlogram with hclust reordering
corrplot(res, type="upper", order="hclust")

#Check data 
#save correlation matrix to long form
library(reshape2)
long_res <- melt(res)


names(wide_top20types)

x <- wide_top20types[,c(17,3)]
a<-x[complete.cases(x),]
names(a)
summary(a)
write.csv(a, "generalCorrelationCompType.csv")

```


###Correlation of average temperture (TAVG) vs top 10 complaint types per zip code

```{r}
library(dplyr)

df_matrix_corr_per_zip <- list()

#remove zip codes which do not have good estimation of top 10 correlations
 remove <- c (10471,10475,10464,11239,10020,10004,10005,10006,10007,10280, 10044,11363,11359,11360, 11104,11693,11694,11695, 11697,11004,11005, 11411,11426, 11427, 11428,10307,10314)
 zipCode <- zipCode [! zipCode %in% remove]


for(i in 1:length(zipCode)) {  
  #filter data by zip code
 
  data_by_zip <- raw_call311_2013to2017 %>%
    select(Incident.Zip, CreatedDate, Type, Freq) %>%
    drop_na() %>%
    filter(Incident.Zip == zipCode[i])
  
  #fix freq = sum(freq) after fxing duplicated complaint type in converison 
  data_by_zip <- data_by_zip %>%
    group_by(Incident.Zip, CreatedDate, Type) %>%
    summarize(
      Freq = sum(Freq)
    )
  
  #calculate top 10 complaint type frequency 
  data_by_zip_total <- data_by_zip %>%
    group_by (Type) %>%
    summarize(
      Total = sum(Freq)
    )
  
  
 data_by_zip_total <- data_by_zip_total %>%
   top_n(n = 10, Total )
  
 #add weather back to the list
 
 Comptype <- as.character(data_by_zip_total$Type)
  data_by_zip <- data_by_zip %>%
    filter (Type %in% c(Comptype, "TAVG","SNOW"))

 
  #transform long form to wide form
   data_by_zip <- spread(data_by_zip,Type,Freq)
   data_by_zip <- data_by_zip %>%
     drop_na() 
   data_by_zip <-data_by_zip[,3:dim(data_by_zip)[2]]
  #calculate correlation by zip code
  cor_data_by_zip <- cor(data_by_zip, use = "complete.obs")
  #save correlation matrix by zip code to a list
  df_matrix_corr_per_zip[[i]] <- cor_data_by_zip

}

 #output correlation matrix by zip code for interputation
 for(i in 1:length(zipCode)) {
   
   tmp_rec <- melt(df_matrix_corr_per_zip[[i]])
   tmp_rec$zipCode <- zipCode[i]
   write.table(tmp_rec, file="corr.csv",sep = ",", append = TRUE)
 }
 
```

### Excel file corr.csv analysis
load interputation

```{r}
weather_compType_zip <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/WeatherCorrelationFinding.csv", header=TRUE, sep=",") 

library(knitr)
kable(weather_compType_zip)

```


###Correlation of Population and median household income by zip code


```{r}

#Prepare raw data sets: read in csv or txt files into R 

pop_inc_zip2017 <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/2017_ComplaintFreq_pop_inc.csv", header=TRUE, sep=",")

#transform long form to wide form
pop_inc_zip2017 <- spread(pop_inc_zip2017,Type,Value)


write.csv(pop_inc_zip2017,"D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/hypothsisTest_High_Inc.csv")

pop_inc_zip2017 <- pop_inc_zip2017[,2:dim(pop_inc_zip2017)[2]]

#calculate correlation by zip code
  cor_pop_inc_zip2017 <- cor(pop_inc_zip2017, use = "complete.obs")

library(corrplot)
# correlogram with hclust reordering
corrplot(cor_pop_inc_zip2017, type="upper", order="hclust")

```


#hypothesis test: Does Higher-income have less number of complaints?
We have 178 mid-household income by zip code in NYC and frequency of 311 calls per zip code in 2017. we use 95% z-test in single tail to validate whether to accept or reject hypothesis.

hypothsis test : 
Ho:  # of complaints of Higher avg income > # of complaints of avg income
Ha :  # of complaints of Higher avg income <= # of complaints of avg income
 
Conclution: reject Ho


```{r}

hypothysis_pop_inc <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/hypothsisTest_High_Inc.csv", header=TRUE, sep=",")

hypothysis_pop_inc <- hypothysis_pop_inc %>%
  select(Zipcode,AvgIncome,ComplaintFreq,Population)%>%
  drop_na()%>%
  filter(AvgIncome != 0, Population !=1 )

averagePopulationIncome= mean(hypothysis_pop_inc$AvgIncome)
averagePopulationComplaintFreq= mean(hypothysis_pop_inc$ComplaintFreq)

highIncome <- hypothysis_pop_inc %>%
    filter(hypothysis_pop_inc$AvgIncome >averagePopulationIncome)

averagehighIncomeComplaintFreq= mean(highIncome$ComplaintFreq)
numHighIncome <- dim(highIncome)[1]

sdHighIncomeComplainFreq <- sd(highIncome$ComplaintFreq)

#Find z score of high midian household income complaint frequency
z_score_highIncomComplainFreq <- (averagehighIncomeComplaintFreq-averagePopulationComplaintFreq)/(sdHighIncomeComplainFreq/sqrt(numHighIncome))


#p-value of high income complaint frequency 
pnorm(z_score_highIncomComplainFreq, lower.tail = TRUE)

```


###Linear regression 

###Average Temperture VS Heat/Hot water complaint frequency.
(daily record is an observation)

```{r}

raw_call311_2013to2017 <- read.csv(file="D:/CUNY_SPS_DA/607_Data_Aq/607 Final Project/goodData/CleanZipCodePerDayComplaintFreq.txt", header=TRUE, sep=",")

#get complaint type = Heat/Hot water total frequency per day

#get average temperture per day (use zipcode 10001 as example)

library(dplyr)
x <- raw_call311_2013to2017 %>%
  filter ( Type == 'HEAT/HOT WATER') %>%
  group_by(CreatedDate, Type) %>%
  summarize(
    Freq = sum(Freq)
  )

y <- raw_call311_2013to2017 %>%
    drop_na() %>%
  filter ( Type == "TAVG"  , Incident.Zip=="10001") %>%
    select(CreatedDate, Type, Freq)

y$Freq <- round(y$Freq,0)

xy<- rbind(as.matrix(x),as.matrix(y))

xy <- spread(data.frame(xy), Type, Freq)

xy$yyyymm <- format(as.Date(xy$CreatedDate, "%m/%d/%Y"), "%Y%m" )

xy <- xy %>% drop_na()

#Month heat/hot water total count
#Avgerage temperture of the month

xy$`HEAT/HOT WATER` <- as.numeric(as.character(xy$`HEAT/HOT WATER`))
xy$TAVG <- as.numeric(as.character(xy$TAVG))


xy2 <- xy %>%
  group_by(yyyymm) %>%
  summarize(
    Month_Sum = sum(`HEAT/HOT WATER`),
    Month_TAVG = mean(TAVG)
  )


lm(xy2$Month_Sum ~ xy2$Month_TAVG)
# numberof Month Heat/Hot Water Complaint = 68728.2 - 905.1* number of Month_TAVG 
# For example, numberof Month Heat/Hot Water Complaint is 23473 when averger temperture is 50 degree.

#Prodetive Modeling - linear regression
plot(xy2$Month_Sum,xy2$Month_TAVG, main="Monthly TAVG-Heat/Hot Water Complaint Frequency", 
  	xlab="Monthly Complaint ", ylab="Monthly Average Temperture (TAVG)" )
lines(lowess(xy2$Month_Sum , xy2$Month_TAVG), col="blue") # lowess line (x,y)

```
